\documentclass[runningheads,a4paper]{llncs}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{tabularx}
\usepackage{fixltx2e}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage[hyphens]{url}
\usepackage{upquote,textcomp}
\lstset{breaklines=true, basicstyle=\scriptsize\ttfamily, upquote=true}

\usepackage{fancyvrb}
\VerbatimFootnotes
\usepackage{cprotect}

\usepackage{graphicx}
\makeatletter
\def\maxwidth#1{\ifdim\Gin@nat@width>#1 #1\else\Gin@nat@width\fi}
\makeatother

\usepackage{amsmath}
\usepackage{pmml-new}

\usepackage{color,graphics,array,csscolor}

\usepackage{fontspec,unicode-math}
\usepackage[Latin,Greek]{ucharclasses}
\setTransitionsForGreek{\fontspec{Times New Roman}}{}

\usepackage{subscript}
\lstset{breaklines=true, basicstyle=\scriptsize\ttfamily}

\begin{document}
\mainmatter

\title{Unleash the Triple: Leveraging a Corporate Discovery Interface: the OECD Case}
\titlerunning{Unleash the Triple}
\author{Mary-Ann Grosset\inst{1} \and
Thierry Vebr\inst{1} \and
Jan-Anno Schuur\inst{1}}
\authorrunning{Mary-Ann Grosset et al.}
\institute{OECD\\
\email{mary-ann.grosset@oecd.org, 
thierry.vebr@oecd.org, 
jan-anno.schuur@oecd.org}}
\maketitle

\begin{abstract}
``O.N.E Sight'', a fully semantic reading assistant developed in the OECD, relies on a semantic layer to enable concept searching. It crawls over millions of resources, consistently tagged to enable discovery of new facts. The use of corporate taxonomies and ontologies, allows you to search using your preferred language and/or vocabulary without having to worry about the language the information is written in, or the words contained in the content. Search in English, find results in French. Search for articles on Agriculture in Australia, and be prompted with information on coastal fishery in Sydney. The semantic layer, allows for the use of discovery algorithms to expand your search with ideas and suggestions and allows you to search for something and find something else of interest that you were not aware of. Search for agriculture in Australia and be prompted to discover content on Agritourism in New South Wales.

\keywords{Linked Data, Semantic Annotation, Semantic Discovery, Semantic Search}
\end{abstract}

\end{document}